Newton's method for finding a root of a differentiable function $f$ takes a guess $x$ and computes hopefully an improved guess as:
$$ x - \frac{f(x)}{Df(x)}$$
where $Df$ denotes the derivative of $f$.

Create a function called `newton_search` with four arguments: `f`, `df`, `guess`, `conv` (the convergence criterion), where `f` is function of interest and `df` is its derivative.
```{r}
newton_search <- function(f, df, guess, conv=0.001) {
# Note: If f does not have a root, we could be in an infinite loop.
  improve <- function(guess, f, df) {
    guess - f(guess) / df(guess)
  }
  while(abs(f(guess)) > conv) {
    guess <- improve(guess, f, df)
  }
  guess
}
```
We pass `f` and `df` as arguments to `newton_serach`. We define a local functions (or helper function) within `newton_search` to compute the improvement and then test for convergence.

Use this function to find the root of $sin(x)$ near 3 using the actual symbolic derivative. The exact answer is $\pi$.
```{r}
newton_search(f = sin, df = cos, guess = 3)
newton_search(f = sin, df = cos, guess = 3, conv = 0.000001)
```
For reference: $\pi$ = `r pi`

In general you may not be able to compute the derivative exactly. Use the symmetric difference quotient to approximate the derivative of $f$ at $x$ numerically by the definition:
$$ Df \approx \frac{f(x + h) - f(x - h)}{2h} $$
for small $h$.

Define a function `make_derivative` with arguments `f` and `h`. The result returned should be a function closure that remembers both `f` and `h`.
```{r}
make_derivative <- function(f, h) {
  function(x) (f(x + h) - f(x - h)) / (2*h)
}
```

Find the root of $sin(x)$ near 3 using numerical derivatives. 
```{r}
Dsin <- make_derivative(f = sin, h = .001)
newton_search(f = sin, df = Dsin, guess = 3)
newton_search(f = sin, df = Dsin, guess = 3, conv = 0.000001)
```

The log-likelihood of the gamma distribution with scale parameter 1 can be written as:
$$ (\alpha -1)s -n\log\Gamma(\alpha) $$
where $\alpha$ is the shape parameter and $s = \sum \log X_i$ is the sufficient statistic.

Randomly draw a sample of $n = 30$ with a shape parameter of $\alpha = 4.5$. Using `newton_search` and `make_derivative`, find the maximum likelihood estimate of $\alpha$. Use the moment estimator of $\alpha$, i.e., $\bar X$ as the initial guess. The log-likelihood function in R is:
```{r}
x <- rgamma(n=30, shape=4.5)

gllik <- function() {
  s <- sum(log(x))
  n <- length(x)
  function(a) {
    (a - 1) * s - n * lgamma(a)
  }
}
```
You must apply `newton_search` to the first and second derivatives (derived numerically using `make_derivative`) of the log-likelihood. The answer should be near 4.5.
```{r}
# The first and second derivatives of the likelihood:
dgllik <- make_derivative(gllik(), 0.001)
ddgllik <- make_derivative(dgllik, 0.001)

# The mle
newton_search(f = dgllik, df = ddgllik, guess = mean(x))
```
Note: The moment estimator is `r mean(x)`


